---
title: "CaFC Profitability Assessment"
author: "Andrew Meter"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
### Libraries
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
library(dplyr)
library(viridis)
```
```
# Setting parameters for scenarios

## Starmaya - Production costs and yields

```{r message=FALSE, warning=FALSE}
#Renovation costs
rC_starmaya=3458
#Production costs year 1 to 12
pC_starmaya=c(0,0,1296,1800,2520,1800,1200,1296,1800,2160,1800,1200)
#Yields (kg/ha)
y_starmaya=c(0,0,993,1380,1932,1380,0,933,1380,1656,1380,0)
```

## local_variety - Production costs and yields

```{r message=FALSE, warning=FALSE}
#Renovation costs
rC_local_variety=3358
#Production costs year 1 to 12
pC_local_variety=c(0,0,1080,1500,2100,1500,1000,1080,1500,1800,1500,1000)
#Yields (t/ha)
y_local_variety=c(0,0,828,1150,1610,1150,0,828,1150,1380,1150,0)
    
```

## CaFC Credit terms
```{r message=FALSE, warning=FALSE}
#Percentage of revenue from years 3/4/5 shared with producer
R_held=0.5
#Interest rate of crédit
#interest_rate_cafc=0.1
# Start year
credit_start_cafc=6
#Number of years
credit_periods_cafc=5
# Function to adjust Revenue, Production Costs and Credit Costs 
cafc_credit<-function(revenue,production_costs,renovation_costs,revenue_held=R_held,interest_rate=interest_rate,start=credit_start_cafc,nbr_periods=credit_periods_cafc){
    
    R_cr=revenue
    R_cr[3]=revenue[3]*revenue_held
    R_cr[4]=revenue[4]*revenue_held
    R_cr[5]=revenue[5]*revenue_held
    
    pC_cr=production_costs
    
    covered_costs=(pC_cr[3]+pC_cr[4]+pC_cr[5])-(R_cr[3]+R_cr[4]+R_cr[5])
    pC_cr[3]=0
    pC_cr[4]=0
    pC_cr[5]=0
    
    if(covered_costs>0){
        tot_credit=renovation_costs+covered_costs
    }else{
        tot_credit=renovation_costs
    }
    
    tot_interests=tot_credit*interest_rate*nbr_periods
    credit_and_interests=tot_credit+tot_interests
    crC=c(0,0,0,0,0,0,0,0,0,0,0,0)
    crC[start:(start+(nbr_periods-1))]=credit_and_interests/nbr_periods
    
    C_cr=pC_cr+crC
    
    results_cr=cbind.data.frame(R_cr,pC_cr,crC,C_cr)
    
    return(results_cr)
}

```
## Price setting mechanisms
```{r message=FALSE, warning=FALSE}
price_setting<-function(price_mechanism,c_price,price_premiums){
if(price_mechanism=="CaFC"){
  price_set=c_price+price_premiums
}else if (price_mechanism=="FT"){
  if(c_price>1.4){
    price_set=c_price+price_premiums
  }else{
    price_set=1.4+price_premiums
  }
} else if(price_mechanism=="Conventional"){
    price_set=c_price+price_premiums
  }
      else{
    print("Choose between price mechanism 'CaFC', 'FT' or 'Conventional'")
  }
  
  return(price_set)
  
}

```


## Local Credit terms
```{r message=FALSE, warning=FALSE}
#Interest rate of crédit
#interest_rate_local=0.2
# Start year
credit_start_local=1
#Number of years
credit_periods_local=5
# Function to adjust Revenue, Production Costs and Credit Costs 
local_credit<-function(revenue,production_costs,renovation_costs,interest_rate=interest_rate,start=credit_start_local,nbr_periods=credit_periods_local){
    R_cr=revenue
    
    pC_cr=production_costs
    
    tot_credit=renovation_costs
        
    tot_interests=tot_credit*interest_rate*nbr_periods
    credit_and_interests=tot_credit+tot_interests
    crC=c(0,0,0,0,0,0,0,0,0,0,0,0)
    crC[start:(start+(nbr_periods-1))]=credit_and_interests/nbr_periods
    
    C_cr=pC_cr+crC
    
    results_cr=cbind.data.frame(R_cr,pC_cr,crC,C_cr)
    
    return(results_cr)
}

```
# Function to build scenarios
The following function builds a scenario based on the following information given
- Variety ("starmaya" or "local_variety")
- Price ($/lbs)
- Credit type ("CaFC credit" or "Local credit")
- Discount rate (%) to be applied when calculating NPV and B/C ratio

The function returns:
- a dataframe with results from year 1 to 12 for revenue, production costs, credit costs, total costs, net margin, accumulated net margin, Benefits (discounted), Costs (discounted), Net profit (discounted)
- NPV
- B/C ratio
```{r message=FALSE, warning=FALSE}
build_scenario<-function(variety="starmaya",price_mechanism="CaFC",c_price="1.0",price_premiums=0.9,interest_rate=0.1,credit_type="CaFC credit",discount_rate=10){
    ## base Revenues anc production costs based on variety
  price=price_setting(price_mechanism = price_mechanism,c_price = c_price,price_premiums = price_premiums)  
  if (variety=="starmaya"){
        R=y_starmaya*(price/0.46)
        pC=pC_starmaya
        rC=rC_starmaya
    } else if(variety=="local"){
        R=y_local_variety*(price/0.46)
        pC=pC_local_variety
        rC=rC_local_variety
    }else{
        print("Choose a variety between starmaya or local")
    }
    
    if(credit_type=="CaFC credit"){
        results=cafc_credit(revenue = R,production_costs = pC,
                            renovation_costs = rC,interest_rate=interest_rate)
    }else if(credit_type=="Local credit"){
        results=local_credit(revenue = R,production_costs = pC,
                             renovation_costs = rC,interest_rate=interest_rate)
    }else{
        print("Choose a credit type between CaFC credit or Local credit")
    }
    # Calculating net margin and accumulated net margin
    results$netmargin=results$R_cr-results$C_cr
    results$accum_netmargin=cumsum(results$netmargin)
    
    # calculate NPV and B/C ratio
    #Discount rate
    r=as.numeric(discount_rate/100)
    #time period
    n=12
    
    results$Benefits=0
    #Discounted Benefits for B/C ratio
    for(i in seq(1:n)){
        results[i,]$Benefits=(results[i,]$R_cr)/((1+r)^i)
    }
    
    results$Costs=0
    #Discounted Costs for B/C ratio
    for(i in seq(1:n)){
        results[i,]$Costs=(results[i,]$C_cr)/((1+r)^i)
    }
    
    # Discounted net margin for NPW
    results$BC=0
    #Discounted Costs for B/C ratio
    for(i in seq(1:n)){
        results[i,]$BC=(results[i,]$netmargin)/((1+r)^i)
    }
    
    results$accum_BC=cumsum(results$BC)
    # NPV
    NPV=sum(results$BC)
    
    BC_ratio=(sum(results$Benefits))/(sum(results$Costs))
    
    ls_results=c(results,NPV,BC_ratio)
    
    return(ls_results)
}

```
# Net Present Value and Benefit/Costs ratios
## Scenario 1

```{r message=FALSE, warning=FALSE}
## variety
variety_S1="starmaya"
## Price
price_mechanism_S1="CaFC"
c_price=1.1
price_premiums_S1=(0.7+0.2)
##setting interest rate and credit type
interest_rate_S1=0.1
credit_type_S1="CaFC credit"
## setting discount rate for NPV and B/C ratio
discount_rate_S1=10
results_S1=build_scenario(variety = variety_S1,price_mechanism = price_mechanism_S1,c_price=c_price,price_premiums = price_premiums_S1,interest_rate=interest_rate_S1,credit_type = credit_type_S1,discount_rate = discount_rate_S1)
results_S1$accum_BC[12]
results_S1[[12]]

```
## Scenario 2

```{r message=FALSE, warning=FALSE}
## variety
variety_S2="local"
## Price
price_mechanism_S2="FT"
c_price=1.1
price_premiums_S2=0.2
##setting interest rate and credit type
interest_rate_S2=0.2
credit_type_S2="Local credit"
## setting discount rate for NPV and B/C ratio
discount_rate_S2=10
results_S2=build_scenario(variety = variety_S2,price_mechanism = price_mechanism_S2,c_price=c_price,price_premiums = price_premiums_S2,interest_rate=interest_rate_S2,credit_type = credit_type_S2,discount_rate = discount_rate_S2)
results_S2$accum_BC[12]
results_S2[[12]]
```
## Scenario 3

```{r message=FALSE, warning=FALSE}
## variety
variety_S3="local"
## Price
price_mechanism_S3="Conventional"
c_price=1.1
price_premiums_S3=0
##setting interest rate and credit type
interest_rate_S3=0.2
credit_type_S3="Local credit"
## setting discount rate for NPV and B/C ratio
discount_rate_S3=10
results_S3=build_scenario(variety = variety_S3,price_mechanism = price_mechanism_S3,c_price=c_price,price_premiums = price_premiums_S3,interest_rate=interest_rate_S3,credit_type = credit_type_S3,discount_rate = discount_rate_S3)
results_S3$accum_BC[12]
results_S3[[12]]
```
# Plotting net margin through 12 years
## Creating dataframe for plotting
```{r message=FALSE, warning=FALSE}
years=as.integer(seq(1:12))
results_S1_plot=as.data.frame(results_S1[1:10])
results_S1_plot$Scenario="Scenario 1"
results_S1_plot$years=years

results_S2_plot=as.data.frame(results_S2[1:10])
results_S2_plot$Scenario="Scenario 2"
results_S2_plot$years=years

results_S3_plot=as.data.frame(results_S3[1:10])
results_S3_plot$Scenario="Scenario 3"
results_S3_plot$years=years

all_results=rbind(results_S1_plot,results_S2_plot,results_S3_plot)
```
## Annual Present Value
```{r message=FALSE, warning=FALSE}

p=  ggplot( data=all_results, aes(x=years,
                            y=BC, group=Scenario, color=Scenario)) +
    geom_hline(yintercept = 0, color = "grey80", size = 1)+
    geom_line(size=1,aes(linetype=Scenario)) +
    scale_linetype_manual(values=c(1,2,4))+
    scale_color_viridis(discrete = TRUE) +
    ggtitle("Annual Present Value per Ha (r = 10%)")+
    scale_x_continuous(breaks=years,limits=c(1,12))+
    theme_clean()+
    theme(legend.title = element_blank(),
          axis.title.x = element_text(size = 15),
          axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))+
    ylab("Present Value (US$/Ha)\n")+
    xlab("\nYear")
    
p

```

## Cumulated Annual Present Value
```{r message=FALSE, warning=FALSE}

p=  ggplot( data=all_results, aes(x=years,
                            y=accum_BC, group=Scenario, color=Scenario)) +
    geom_hline(yintercept = 0, color = "grey80", size = 1)+
    geom_line(size=1,aes(linetype=Scenario)) +
    scale_linetype_manual(values=c(1,2,4))+
    scale_color_viridis(discrete = TRUE) +
    ggtitle("Cumulated Annual Present Value per Ha (r = 10%)") +
    ylab("Cum. Present Value (US$/Ha) \n")+
    xlab("\nYear")+
    scale_x_continuous(breaks=years,limits=c(1,12))+
    theme_clean()+
    theme(legend.title = element_blank(),
          axis.title.x = element_text(size = 15),
          axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))
p


```
# Sensitivity analysis
## Price sensitivity
### Functions for price sensitivity analysis
```{r message=FALSE, warning=FALSE}
## Scenario 1
price_sensitivity_S1<-function(x){
    list=build_scenario(c_price=x,price_mechanism=price_mechanism_S1,price_premiums=price_premiums_S1,variety = variety_S1,interest_rate=interest_rate_S1,credit_type = credit_type_S1,discount_rate = discount_rate_S1)
    return(list$accum_BC[12])
}
price_sensitivity_S1 <- Vectorize(price_sensitivity_S1)

## Scenario 2
price_sensitivity_S2<-function(x){
    list=build_scenario(c_price=x,price_mechanism=price_mechanism_S2,price_premiums=price_premiums_S2,variety = variety_S2,interest_rate=interest_rate_S2,credit_type = credit_type_S2,discount_rate = discount_rate_S2)
    return(list$accum_BC[12])
}
price_sensitivity_S2 <- Vectorize(price_sensitivity_S2)

## Scenario 3
price_sensitivity_S3<-function(x){
    list=build_scenario(c_price=x,price_mechanism=price_mechanism_S3,price_premiums=price_premiums_S3,variety = variety_S3,interest_rate=interest_rate_S3,credit_type = credit_type_S3,discount_rate = discount_rate_S3)
    return(list$accum_BC[12])
}
price_sensitivity_S3 <- Vectorize(price_sensitivity_S3)

```
### Ploting results of price sensitivity analysis
```{r message=FALSE, warning=FALSE}
#results for c-price=0.9;1.1;1.5
Price_sensitivity_0.8=c(price_sensitivity_S1(0.9),price_sensitivity_S2(0.9),price_sensitivity_S3(0.9))
Price_sensitivity_1.1=c(price_sensitivity_S1(1.1),price_sensitivity_S2(1.1),price_sensitivity_S3(1.1))
Price_sensitivity_1.5=c(price_sensitivity_S1(1.5),price_sensitivity_S2(1.5),price_sensitivity_S3(1.5))
Price_sensitivity_0.8
Price_sensitivity_1.1
Price_sensitivity_1.5
#setting minimum and maximum c-price for sensitivity analysis
min_c_price=0.5
max_c_price=2
#plot results
p=ggplot(data.frame(x=c(min_c_price,max_c_price)), aes(x=x)) + 
    stat_function(fun=price_sensitivity_S1,colour = viridis(3,alpha = 0.8)[1],size=1,linetype=1)+
    stat_function(fun=price_sensitivity_S2,colour=viridis(3,alpha = 0.8)[2],size=1,linetype=2)+
    stat_function(fun=price_sensitivity_S3,colour=viridis(3,alpha = 0.8)[3],size=1,linetype=3)
 p=p+
   geom_hline(yintercept = 0, color = "grey80", size = 1)+
    ggtitle("Variation of NPV depending on c-price") +
    ylab("Net Present Value (US$/Ha)\n")+
    xlab("\nC-price (US$/lbs)")+
    scale_x_continuous(breaks=seq(min_c_price,max_c_price,by=0.2),limits=c(min_c_price,max_c_price))+
    theme_clean()+
    theme(legend.title = element_blank(),
          axis.title.x = element_text(size = 15),
          axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))
 p
   
```


## Discount sensitivity
### Functions for Discount rate sensitivity analysis
```{r message=FALSE, warning=FALSE}
## Scenario 1
discount_rate_sensitivity_S1<-function(x){
    list=build_scenario(discount_rate=x,c_price=c_price,price_mechanism=price_mechanism_S1,price_premiums=price_premiums_S1,variety = variety_S1,interest_rate=interest_rate_S1,credit_type = credit_type_S1)
    return(list$accum_BC[12])
}
discount_rate_sensitivity_S1 <- Vectorize(discount_rate_sensitivity_S1)

## Scenario 2
discount_rate_sensitivity_S2<-function(x){
    list=build_scenario(discount_rate=x,c_price=c_price,price_mechanism=price_mechanism_S2,price_premiums=price_premiums_S2,variety = variety_S2,interest_rate=interest_rate_S2,credit_type = credit_type_S2)
    return(list$accum_BC[12])
}
discount_rate_sensitivity_S2 <- Vectorize(discount_rate_sensitivity_S2)

## Scenario 3
discount_rate_sensitivity_S3<-function(x){
    list=build_scenario(discount_rate=x,c_price=c_price,price_mechanism=price_mechanism_S3,price_premiums=price_premiums_S3,variety = variety_S3,interest_rate=interest_rate_S3,credit_type = credit_type_S3)
    return(list$accum_BC[12])
}
discount_rate_sensitivity_S3 <- Vectorize(discount_rate_sensitivity_S3)
discount_rate_sensitivity_S1(0)
```

### Ploting results of discount rate sensitivity analysis
```{r message=FALSE, warning=FALSE}
#results for discount rate=5%;10%;20%
Discount_rate_sensitivity_5=c(discount_rate_sensitivity_S1(5),discount_rate_sensitivity_S2(5),discount_rate_sensitivity_S3(5))
Discount_rate_sensitivity_10=c(discount_rate_sensitivity_S1(10),discount_rate_sensitivity_S2(10),discount_rate_sensitivity_S3(10))
Discount_rate_sensitivity_20=c(discount_rate_sensitivity_S1(20),discount_rate_sensitivity_S2(20),discount_rate_sensitivity_S3(20))
Discount_rate_sensitivity_5
Discount_rate_sensitivity_10
Discount_rate_sensitivity_20
#setting minimum and maximum discount rate for sensitivity analysis
min_discount_rate=0
max_discount_rate=20
#plot results
p=ggplot(data.frame(x=c(min_discount_rate,max_discount_rate)), aes(x=x)) + 
    stat_function(fun=discount_rate_sensitivity_S1,colour = viridis(3,alpha = 0.8)[1],size=1,linetype=1)+
    stat_function(fun=discount_rate_sensitivity_S2,colour=viridis(3,alpha = 0.8)[2],size=1,linetype=2)+
    stat_function(fun=discount_rate_sensitivity_S3,colour=viridis(3,alpha = 0.8)[3],size=1,linetype=3)

  p=p+
    geom_hline(yintercept = 0, color = "grey80", size = 1)+
    ggtitle("Variation of NPV depending on applied discount rate") +
    ylab("Net Present Value (US$/Ha)\n")+
    xlab("\n% Discount Rate (r)")+
    scale_x_continuous(breaks=seq(min_discount_rate,max_discount_rate,by=2),limits=c(min_discount_rate,max_discount_rate))+
    theme_clean()+
    theme(legend.title = element_blank(),
          axis.title.x = element_text(size = 15),
          axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))
 
p

```




## Interest rate sensitivity
### Functions for interest rate sensitivity analysis
```{r message=FALSE, warning=FALSE}
## Scenario 1
interest_sensitivity_S1<-function(x){
    list=build_scenario(interest_rate=x,c_price=c_price,price_mechanism=price_mechanism_S1,price_premiums=price_premiums_S1,variety = variety_S1,credit_type = credit_type_S1,discount_rate = discount_rate_S1)
    return(list$accum_BC[12])
}
interest_sensitivity_S1 <- Vectorize(interest_sensitivity_S1)

## Scenario 2
interest_sensitivity_S2<-function(x){
    list=build_scenario(interest_rate=x,c_price=c_price,price_mechanism=price_mechanism_S2,price_premiums=price_premiums_S2,variety = variety_S2,credit_type = credit_type_S2,discount_rate = discount_rate_S2)
    return(list$accum_BC[12])
}
interest_sensitivity_S2 <- Vectorize(interest_sensitivity_S2)

## Scenario 3
interest_sensitivity_S3<-function(x){
    list=build_scenario(interest_rate=x,c_price=c_price,price_mechanism=price_mechanism_S3,price_premiums=price_premiums_S3,variety = variety_S3,credit_type = credit_type_S3,discount_rate = discount_rate_S3)
    return(list$accum_BC[12])
}
interest_sensitivity_S3 <- Vectorize(interest_sensitivity_S3)

```
### Ploting results of interest rate sensitivity analysis
```{r message=FALSE, warning=FALSE}
#results for interest rate=10%,20%,30%
interest_sensitivity_10=c(interest_sensitivity_S1(0.1),interest_sensitivity_S2(0.1),interest_sensitivity_S3(0.1))
interest_sensitivity_20=c(interest_sensitivity_S1(0.2),interest_sensitivity_S2(0.2),interest_sensitivity_S3(0.2))
interest_sensitivity_30=c(interest_sensitivity_S1(0.3),interest_sensitivity_S2(0.3),interest_sensitivity_S3(0.3))
interest_sensitivity_10
interest_sensitivity_20
interest_sensitivity_30
#setting minimum and maximum interest rate for sensitivity analysis
min_interest_rate=0.05
max_interest_rate=0.3
#plot results
p=ggplot(data.frame(x=c(min_interest_rate,max_interest_rate)), aes(x=x)) + 
    stat_function(fun=interest_sensitivity_S1,colour = viridis(3,alpha = 0.8)[1],size=1,linetype=1)+
    stat_function(fun=interest_sensitivity_S2,colour=viridis(3,alpha = 0.8)[2],size=1,linetype=2)+
    stat_function(fun=interest_sensitivity_S3,colour=viridis(3,alpha = 0.8)[3],size=1,linetype=3)
 p=p+
   geom_hline(yintercept = 0, color = "grey80", size = 1)+
    ggtitle("Variation of NPV depending on interest rate of loan") +
    ylab("Net Present Value (US$/Ha)\n")+
    xlab("\nInterest rate of loan")+
    scale_x_continuous(breaks=seq(min_interest_rate,max_interest_rate,by=0.05),limits=c(min_interest_rate,max_interest_rate))+
    theme_clean()+
    theme(legend.title = element_blank(),
          axis.title.x = element_text(size = 15),
          axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))
 p
 
```
### Ploting Costs and revenues for different 
```{r message=FALSE, warning=FALSE}

   
```